Molecular dynamics simulation of synchronization in driven particles

### 2020-12-17 manuscript/manuscript_ajp_2020.tex
read C&C very helpful 2018 skyrmion paper

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
that can be modeled with numerical studies of confined 
driven particles.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Examples of synchronization occur
in many natural periodic systems,
from Huygens 1665 observation of
in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
to fireflies signaling in time with a pulsed light emitting diode \cite{},
to coordinated flapping of birds wings \cite{},
to simultaneous neuronal firing in cardiac muscle \cite{}
and brain tissue \cite{}.

%phase locking
Dynamical mode locking is a controlled 
synchronization phenomena in 
which an external driving force
causes
%the natural oscillation frequencies
%in
weakly coupled oscillators to come into phase.
Mode locking is often observed in quantum electronic
devices such as Josephson junctions \cite{}
and phase-locked current loops \cite{}.
Instead of ohmic current-voltage (I-V) relationships,
such devices exhibit stepped regions
such as Shapiro steps \cite{} [explain].

@@

\begin{table}[h!]
\centering
\caption{Simulation units defined in the code.}
\begin{ruledtabular}
\begin{tabular}{c c p{5cm}}
Quantity & Unit \\
\hline
length &  $a_0$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
dimensionless interaction strength & $q$ \\
effective colloidal charge & $Z^*$ \\
solvent dielectic constant & $\epsilon \epsilon_0$\\
force & $E_0 / a_0$\\
viscosity/damping constant & $\eta$ \\
time &  $\eta / E_0$ \\
velocity &  $ E_0 / \eta a_0$ \\
\end{tabular}
\end{ruledtabular}
\label{tab:1}
\end{table}

We model particle interaction forces
$\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$ 
with
the Yukawa potential energy 
\begin{equation}
  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
\end{equation}
where particle $i$ and $j$ are distance
$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
This 
screened Coulomb potential
%$E_0=2$ scales strength of repulsion
is scaled in terms of energy unit $E_0$
defined in Table ~\ref{tab:1}.
%$ = k q_1 q_2$. %[CHECK scaling/units].
$\kappa = 1/R_0$ is the screening parameter 
that describes the lengthscale at
which particles interact.
We fix $R_0$ to be $a_0$.
In experiments charge screening is observed
due to ions in the suspending fluid and
the charges of surrounding particles
which
reduces the interaction range of individual particles. % \cite{}.
Because the particles interact over short ranges, 
the numerical models can be run efficiency
using a neighbor list algorithm
determined using a cell method.
[explain!]

@@

We use several model enviroments to confine the particles,
assuming the confining force arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 $\vec{F}_{l}(\vec{r}) = -\nabla V_l(\vec{r}).$
 The landscape potential $V(\vec{r}) $ are static 
 with fixed minima and maxima
 that are periodic or quasi-periodic,
 as described in Sec.~\ref{sec:results}.
% 
% One example of a periodic landscape is
%% %that used in Sec.~\ref{sec:one}
% where 
% \begin{equation}
%   V_l(y) = V_0 \cos{(N_p \pi y / L)}
% \end{equation}
% where $N_p$ are the number of periods,
% and $V_0$ is an adjustable parameter
% to set the depth of the troughs.
%
 In multi-particle simulations, we confine
 the particles along the $x-$direction 
 using a periodic function 
 \begin{equation}
   V_{q1D}(x) = V_0 \cos{(\pi x / L)}
 \end{equation}.
 %%We could also use a Gaussian function.
 This channel potential keeps the particles
 interacting at short range confined primarily to motion
 along the y-direction
 but allows for some lateral motion of particles.
 This is sometimes referred to as a
 quasi-one-dimensional geometry.

@@

>>>>

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
that can be modeled with numerical studies of confined 
driven particles.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Examples of synchronization occur
in many biological systems with periodic behavior,
from fireflies signaling in time with a pulsed light emitting diode \cite{},
to coordinated flapping of birds wings \cite{},
to simultaneous firing of neurons in cardiac muscle \cite{}
and brain tissue \cite{}.

Huygens 1665 observation of
in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
to

%phase locking

Either coupled oscillators or a single particle on a corrugated
potential with an applied AC drive.

Relationship between substrate period and intrinsic velocity
with phase locking caused by AC force modulates drive
where the particle velocity is constant even though the applied
DC force is increased.

Particles - velocity-force curves
Josephson Junctions - voltage-current curves

what distinguishes a Shapiro step?
where else are they witnessed?

Dynamical mode locking is a controlled 
synchronization phenomena in 
which an external driving force
causes
%the natural oscillation frequencies
%in
weakly coupled oscillators to come into phase.
Mode locking is often observed in quantum electronic
devices such as Josephson junctions \cite{}
and phase-locked current loops \cite{}.
Instead of ohmic current-voltage (I-V) relationships,
such devices exhibit stepped regions
such as Shapiro steps \cite{} [explain].

@@

\begin{table}[h!]
\centering
\caption{Simulation units.}
\begin{ruledtabular}
\begin{tabular}{c c p{5cm}}
Quantity & Unit \\
\hline
length &  $a_0$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
dimensionless interaction strength & $q$ \\
effective colloidal charge & $Z^*$ \\
solvent dielectic constant & $\epsilon \epsilon_0$\\
force & $E_0 / a_0$\\
viscosity/damping constant & $\eta$ \\
time &  $\eta / E_0$ \\
velocity &  $ E_0 / \eta a_0$ \\
\end{tabular}
\end{ruledtabular}
\label{tab:1}
\end{table}

We model particle interaction forces
$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
with
the Yukawa potential energy 
\begin{equation}
  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
\end{equation}
where particle $i$ and $j$ are distance
$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
This 
screened Coulomb potential
%$E_0=2$ scales strength of repulsion
is scaled in terms of energy unit $E_0$
defined in Table ~\ref{tab:1}.
%$ = k q_1 q_2$. %[CHECK scaling/units].
$\kappa = 1/R_0$ is the screening parameter 
that describes the lengthscale at
which particles interact.
We fix $R_0$ to be $a_0$.
In experiments charge screening is observed
due to ions in the suspending fluid and
the charges of surrounding particles
which
reduces the interaction range of individual particles. % \cite{}.
Because the particles interact over short ranges, 
the numerical models can be run efficiency
using a neighbor list algorithm
determined using a cell method.
[explain!]

@@

We use several model enviroments to confine the particles,
assuming the confining force arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 $\vec{F}_{l}(\vec{r}) = -\nabla V_l(\vec{r}).$
 The landscape potential $V(\vec{r}) $ are static 
 with fixed minima and maxima
 that are periodic or quasi-periodic,
 as described in Sec.~\ref{sec:results}.
% 
% One example of a periodic landscape is
%% %that used in Sec.~\ref{sec:one}
% where 
% \begin{equation}
%   V_l(y) = V_0 \cos{(N_p \pi y / L)}
% \end{equation}
% where $N_p$ are the number of periods,
% and $V_0$ is an adjustable parameter
% to set the depth of the troughs.
%
 In multi-particle simulations, we confine
 the particles along the $x-$direction 
 using a periodic function 
 \begin{equation}
   U_{q1D}(x) = U_0 \cos{(\pi x / L)}
 \end{equation}.
 %%We could also use a Gaussian function.
 This 
 quasi-one-dimensional geometry
 confines the particles
 primarily to move 
 along the y-direction
 but allows for some lateral motion of particles.
 Otherwise the repulsive interaction between
 particles would cause them to spread throughout the system.

@@

  \bibitem{} Reichhardt, C., & Reichhardt, C. J. O. (2015). Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives. Physical Review B - Condensed Matter and Materials Physics, 92(22). https://doi.org/10.1103/PhysRevB.92.224432
